\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\title{Iteration 0 Report}
\author{Kaiyuan (Kelvin) Gao, Hanson Yu\\ Pengcheng Liao, Junru Liu, Winston Liu, Lucas Lyu}
\date{September 23, 2022}

\begin{document}

\maketitle
\tableofcontents
\pagebreak

\section{Roles}
The following section summarizes key stakeholders.

\subsection{JJGroupLease}
JJLeaseGroup is our team's customer. Taken from their existing website, their About Us and Mission Statement is as follows:
\begin{quote}
We are a professional team lead by Jennifer Juang, an agent and locator of Texas Association of Realtors. We not only provide free consulting of leasing but also the residential and commercial sales. Our goal is to help all of you to find a sweet and warm home in Texas. We look forward to meeting you and finding you your perfect place.
\end{quote}

\subsection{Our Team}
For this project Kelvin will serve as the Scrum Master and Hanson will serve as the Product Owner. Everyone has equal responsibility with developing the software.

\section{Meetings}
Our meetings are usually conducted via Zoom. Depending on availability, the meetings may also be conducted in person.

\subsection{Meeting 1}
Our first meeting with the customer, was on September 13th, 2022 at 8:00PM CST on \href{https://tamu.zoom.us/rec/share/kEgygyjCLgkbudjWJ6mxFOQvCbwMZURmFh5FwdnvB8K65vDr9X2wrg7qcIK0lOGj.kSFXOVHrF6uZ0hzF?startTime=1663117169000}{Zoom} (Password: 3KZ!jPwp).

\pagebreak

\section{Summary}
The customer, JJLeaseGroup, currently has a website built through Wix for helping students find housing near Universities. The page has very little functionality. The customer currently has two main requirements. The first requirement is to add an interactive map to their website that allows potential tenants to view available properties within a region. The second requirement is have a scheduling functionality where interested tenants can contact JJLeaseGroup with inquiries on the property.\\

\noindent As mentioned previously, neither of the major requirements exist on their current page. Our team will develop an application that will meet both needs and more. Our plan for the first requirement include adding an interactive map that has many functionalities such as allowing for searching and filters. For the second requirement, we temporary plan is to add a scheduling mechanism similar to \href{https://www.when2meet.com/}{when2meet}. Depending on customer needs, this feature could also come with other possible components such as real time chat, email, or WeChat.

\section{Links}
Below are the relevant links for our project.
\begin{itemize}
    \item[-]
        \href{https://github.tamu.edu/hyu/jjleasegroup}{GitHub}
    \item[-]
        \href{https://www.pivotaltracker.com/projects/2595494}{Pivotal Tracker}
    \item[-]
        \href{https://teams.microsoft.com/l/team/19%3aXWjtCUqGt6RxXxkIr3OSatS0eA3LvTel_hHg7H4RVWU1%40thread.tacv2/conversations?groupId=3f3b5b0c-fd70-4614-8136-268b05825fac&tenantId=68f381e3-46da-47b9-ba57-6f322b8f0da1}{Microsoft Teams}

    \item[-]
        \href{https://x9shpyf80h.larksuite.com/drive/folder/fldusCrHhDEsuBDbmFOMmDk8PGI}{Lark}
\end{itemize}

\end{document}
